---
title: "p8105_hw1_tl3391"
author: "Tong Liu"
date: "2025-09-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moderndive)
data("early_january_weather")
```
##Problem 1
```{r}
names(early_january_weather)
summary(early_january_weather$temp)
summary(early_january_weather$humid)
summary(early_january_weather$wind_speed)
summary(early_january_weather$pressure)
```
The variables include origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. 
For temp, the min value is 24.08, the max value is 57.92, and the meadian is 39.02, the mean is 39.58
For humid, the min value is 32.86, the max value is 100, and the median is 61.67, the mean is 65.48
For wind_speed, the min value is 0, the max value is 24.166, the median is 8.055, the mean is 8.226
For pressure, the min value is 1011, the max value is 1034, the median is 1022, the mean is 1023
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
There are 358 rows and 15 columns in the dataset.
```{r}
mean(early_january_weather$temp)
```
The mean temperature is 39.58212

```{r}
library(ggplot2)
p = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time",
    x = "Time",
    y = "Temperature"
  )
```

##Problem 2
```{r}
set.seed(123)
num  = rnorm(10)
logivec = num > 0
char = letters[1:10]
fac = factor(sample(c("A", "B", "C"), size = 10, replace = TRUE))
```

```{r}
mean(num)
mean(logivec)
mean(char)
mean(fac)
```
There are outputs for num and logivec, but the results are NA for character and factor vector.

```{r}
logivec_num  = as.numeric(logivec)    
char_num  = as.numeric(char)    
fac_num  = as.numeric(fac)   
```
The logical vector turns in to 1 and 0 from True and False,and factor vector turns into 1,2, and 3 from A, B, and C. However, the char all become NA.The reason we are not getting the mean for char and factor vector is because they are characters and not numerical values, if we change the format of values into numerical values, we will be able to use operation functions to it.
